---
title: "visr meta 20201224"
author: "Sofia Danna"
date: "December 24, 2020"
output: html_document
---


# Mise en place

* Analysis: 
    + The following tutorial was used for analyses: <https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/> 
    + Main analyses are random effects models; subgroup analyses are fixed effects models.

* Data
    + The visr dataframe was created based on ORs collected from the vocational interventions systematic review. Different estimates may overlap in different analyses, so columns beginning with rep_ were added to help eliminate estimates that need to be removed for each analysis (i.e., rep_xxx for the xxx subgroup analysis of joint estimates).

```{r}
# On Sofia's Douglas Windows computer
#neet <- read.csv("C:/Users/dansof/Dropbox/PEPP new/NEET meta-analysis/metaanalysis/neet 20200525.csv")

# On Sofia's personal Mac
visr <- read.csv("~/Dropbox/PEPP/vocational interventions SR - VISR/6 Analysis/VISR meta-analysis/visr_meta/ORs 20210105.csv")
```

checking out the variables in the dataframe
```{r}
visr
str(visr)
```

installing and loading meta package
```{r message=FALSE, warning=FALSE}
install.packages("meta", repos = "http://cran.us.r-project.org")
install.packages("dplyr", repos = "http://cran.us.r-project.org")
library(meta)
library(metafor)
library(dplyr)
```

Parameter       | Function
----------------|---------------------------------------------------------------------------------
TE	            | This tells R to use the TE column to retrieve the effect sizes for each study
seTE	          | This tells R to use the seTE column to retrieve the standard error for each study
data=	          | After =, paste the name of your dataset here
studlab=paste()	| This tells the function were the labels for each study are stored. If you named the spreadsheet columns as advised, this should be studlab=paste(Author)
comb.fixed=	    | Whether to use a fixed-effects-model
comb.random=	  | Whether to use a random-effects-model. This has to be set to TRUE
method.tau=	    | Which estimator to use for the between-study variance
hakn=	          | Whether to use the Knapp-Hartung method
prediction=	    | Whether to print a prediction interval for the effect of future studies based on present evidence
sm=	            | The summary measure we want to calculate. We can either calculate the mean difference (MD) or Hedges’ g (SMD)

Using the instructions from the tutorial by Mathias Harrer (url above),

instead of | we will use
-----------|-----------
"Author"   | "study"
"TE"       | "OR_ln"
"seTE"     | "SE"

# Analyses: Main outcomes

## EMPLOYMENT

```{r}
emp <- filter(visr, emp==1) #  & is.na(rep_emp)==TRUE)

emp

meta.emp <- metagen(OR_ln,
                    SE,
                    data=emp,
                    studlab=paste(study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.emp

forest(meta.emp)
```

***

## EDUCATION 

```{r}
edu <- filter(visr, edu==1) #& is.na(rep_edu))

edu

meta.edu <- metagen(OR_ln,
                     SE,
                     data=edu,
                     studlab=paste(study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.edu

forest(meta.edu)
```

***

## JOINT

```{r}
joint <- filter(visr, emp_edu==1) #is.na(rep_joint))

joint

meta.joint <- metagen(OR_ln,
                    SE,
                    data=joint,
                    studlab=paste(study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.joint

forest(meta.joint)
```

### EDUCATION - design

```{r}
joint.des <- filter(visr, emp_edu==1) #is.na(rep_joint))

joint.des

meta.joint.des <- metagen(OR_ln,
                        SE,
                        data=joint.des,
                        studlab=paste(study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.joint.des<-update.meta(meta.joint.des,
                          byvar=design, 
                          comb.random = F, 
                          comb.fixed = T)

meta.joint.des

forest(meta.joint.des)
```

### JOINT - intervention

```{r}
joint.inter <- filter(visr, emp_edu==1)

joint.inter

meta.joint.inter <- metagen(OR_ln,
                        SE,
                        data=joint.inter,
                        studlab=paste(study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.joint.inter<-update.meta(meta.joint.inter, 
                          byvar=intervention, 
                          comb.random = F, 
                          comb.fixed = T)

meta.joint.inter

forest(meta.joint.inter)
```

### JOINT - mental health problem

```{r}
joint.mh <- filter(visr, emp_edu==1)

joint.mh

meta.joint.mh <- metagen(OR_ln,
                        SE,
                        data=joint.mh,
                        studlab=paste(study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.joint.mh<-update.meta(meta.joint.mh, 
                          byvar=mhp, 
                          comb.random = F, 
                          comb.fixed = T)

meta.joint.mh

forest(meta.joint.mh)
```

### JOINT - control

```{r}
joint.con <- filter(visr, emp_edu==1)

joint.con

meta.joint.con <- metagen(OR_ln,
                        SE,
                        data=joint.con,
                        studlab=paste(study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.joint.con<-update.meta(meta.joint.con, 
                          byvar=control, 
                          comb.random = F, 
                          comb.fixed = T)

meta.joint.con

forest(meta.joint.con)
```

***
